---
title: Prediction Example
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/Prediction-",
  out.width = "100%"
)
```

### Data

Consider the following gruped data consisting of the number of detected bugs per day in 18 working days.

```{r example5}
### require load librareis; Rsrat and Rphsrm
library(Rphsrm)

### Observed data
fault <- c(0, 1, 0, 5, 0, 0, 2, 1, 1, 0, 6, 4, 0, 0, 0, 6, 3, 3)
```

### Prediction

Estimate and determine an SRM from 11 ordinary models using Rsrat.

```{r example6}
## all results
result0 <- fit.srm.nhpp(fault=fault, selection=NULL)
result0

## the model with minimum AIC
minaic0 <- result0[[which.min(sapply(result0, function(m) m$aic))]]
minaic0
```

The prediction for the number of bugs after 18 working days is given as folows.

```{r example7}
sapply(result0, function(m) m$srm$mvf(t=19:33)) # The cumulative number of bugs up to 33 days
sapply(result0, function(m) m$srm$dmvf(t=18:33)[-1]) # The number of bugs per day after 18 days
```

Next we try to use CPHSRM for the prediction. Estimate CPHSRM with 50 phases.

```{r example8}
## all results
result1 <- fit.srm.cph(fault=fault, phase=seq.int(5,100,5), selection=NULL)
result1

## the model with minimum AIC
minaic1 <- result1[[which.min(sapply(result1, function(m) m$aic))]]
minaic1
```

The prediction for the number of bugs after 18 working days is given as folows.

```{r example9}
sapply(result1, function(m) m$srm$mvf(t=19:33)) # The cumulative number of bugs up to 33 days
sapply(result1, function(m) m$srm$dmvf(t=18:33)[-1]) # The number of bugs per day after 18 days
```

### Verification

Now we have the real data after 19 days.

```{r example10}
fault19 <- c(4, 2, 6, 2, 0, 6, 1, 2, 0, 1, 1, 1, 0, 0, 0)
```

Compute the predictive errors

```{r example12}
observed <- cumsum(fault)
future <- sum(fault) + cumsum(fault19)

create.table <- function(result) {
  lse <- function(m) {
    sum((m$srm$mvf(t = 1:18) - observed)^2)/length(observed)
  }
  
  pse <- function(m) {
    sum((m$srm$mvf(t = 19:33) - future)^2)/length(future)
  }
  
  psed <- function(m) {
    sum((m$srm$dmvf(t = 18:33)[-1] - fault19)^2)/length(fault19)
  }
  data.frame(
    NAME=sapply(result, function(m) m$srm$name),
    LSE=sapply(result, lse),
    AIC=sapply(result, function(m) m$aic),
    PSE=sapply(result, pse),
    PSEd=sapply(result, psed)
  )
}

show(create.table(result0))
show(create.table(result1))
```

Draw the graph for the cumulative number of bugs with the minimum pse models.

```{r example11}
mvfplot(fault=c(fault, fault19), mvf=list(result0$lxvmax$srm, result1$cph70$srm))
dmvfplot(fault=c(fault, fault19), dmvf=list(result0$lxvmax$srm, result1$cph70$srm))
```

