---
output:
  github_document:
    df_print: "kable"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# Rphsrm

Rphsrm provides the package to evalute the software reliability from the fault data collected in the testing phase. Rphsrm uses two types of data; fault-detection time data and its grouped data. The fault-detection time data is a sequence of time intervals of fault detection times (CPU time, etc). Also its grouped data is a sequence of the number of detected faults for each time interval (per a working day, per a week, etc). The reliability evaluation is based on the software reliability growth model called PHSRM which is defined by NHPP (non-homogeneous Poisson process)
with phase-type fault-detection time distribution.

## Installation

You can install Rphsrm from GitHub with:

```{r gh-installation, eval = FALSE}
install.packages("devtools")
devtools::install_github("SwReliab/Rphsrm")
```

Alternatively, you can install Rphsrm with remote:

```{r gh-installation2, eval = FALSE}
install.packages("remotes")
remotes::install_github("SwReliab/Rphsrm")
```

## Example

This is an example of the estimation of software reliability growth models from a fault data (tohma). 

```{r example1}
### load Rphsrm
library(Rphsrm)

### load example data that is included in Rsrat
data(dacs)

### tohma is a grouped data
tohma

### Esimate all models and select the best one in terms of AIC
(result <- fit.srm.cph(fault=tohma))

### Draw the graph 
mvfplot(fault=tohma, srms=result)
```

The second example illustrates the estimation for the model with user-specified phases

```{r example2}
### Estimate two models and no select
(result <- fit.srm.cph(fault=tohma, phase=c(3, 50), selection=NULL))

### Draw the graph
mvfplot(fault=tohma, srms=result)

### Draw the graph (dmvf)
dmvfplot(fault=tohma, srms=result)
```

The third example shows the case where the fault data are fault detection data.

```{r example3}
### fault-detection time data
#### Time intervals for all faults
#### The last value is a negative value, that indicates the time interval in which there is no fault detection after the last fault detection.
sys1

### Esimate
(result <- fit.srm.cph(time=sys1[sys1>=0], te=-sys1[sys1<0]))

### Draw the graph
mvfplot(time=sys1[sys1>=0], te=-sys1[sys1<0], srms=result)
```

The fourth example illustrates the case where the mvfs for all the models are drawn.

```{r example4}
### Esimate and return all the estimated results
(result <- fit.srm.cph(fault=sys1g, phase=c(1,2,3,4,5,10,20,50,100), selection=NULL))

### Draw the graph
mvfplot(fault=sys1g, srms=result)
```

## Prediction Example

### Data

Consider the following gruped data consisting of the number of detected bugs per day in 18 working days.

```{r example5}
### Observed data
fault <- c(0, 1, 0, 5, 0, 0, 2, 1, 1, 0, 6, 4, 0, 0, 0, 6, 3, 3)
```

### Prediction

Estimate and determine an SRM from 11 ordinary models using Rsrat.

```{r example6}
## all results
result0 <- fit.srm.nhpp(fault=fault, selection=NULL)
result0

## the model with minimum AIC
minaic0 <- result0[[which.min(sapply(result0, function(m) m$aic))]]
minaic0
```

The prediction for the number of bugs after 18 working days is given as folows.

```{r example7}
sapply(result0, function(m) mvf(19:33, m)) # The cumulative number of bugs up to 33 days
sapply(result0, function(m) dmvf(18:33, m)[-1]) # The number of bugs per day after 18 days
```

Next we try to use CPHSRM for the prediction. Estimate CPHSRM with 50 phases.

```{r example8}
## all results
result1 <- fit.srm.cph(fault=fault, phase=seq.int(5,100,5), selection=NULL)
result1

## the model with minimum AIC
minaic1 <- result1[[which.min(sapply(result1, function(m) m$aic))]]
minaic1
```

The prediction for the number of bugs after 18 working days is given as folows.

```{r example9}
sapply(result1, function(m) mvf(19:33, m)) # The cumulative number of bugs up to 33 days
sapply(result1, function(m) dmvf(18:33, m)[-1]) # The number of bugs per day after 18 days
```

### Verification

Now we have the real data after 19 days.

```{r example10}
fault19 <- c(4, 2, 6, 2, 0, 6, 1, 2, 0, 1, 1, 1, 0, 0, 0)
```

Compute the predictive errors

```{r example12}
observed <- cumsum(fault)
future <- sum(fault) + cumsum(fault19)

create.table <- function(result) {
  lse <- function(m) {
    sum((mvf(1:18, m) - observed)^2)/length(observed)
  }
  
  pse <- function(m) {
    sum((mvf(19:33, m) - future)^2)/length(future)
  }
  
  psed <- function(m) {
    sum((dmvf(18:33, m)[-1] - fault19)^2)/length(fault19)
  }
  data.frame(
    NAME=sapply(result, function(m) m$srm$name),
    LSE=sapply(result, lse),
    AIC=sapply(result, function(m) m$aic),
    PSE=sapply(result, pse),
    PSEd=sapply(result, psed)
  )
}

create.table(result0)
create.table(result1)
```

Draw the graph for the cumulative number of bugs with the minimum pse models.

```{r example11}
mvfplot(fault=c(fault, fault19), srms=list(result0$lxvmax, result1$cph70))
dmvfplot(fault=c(fault, fault19), srms=list(result0$lxvmax, result1$cph70))
```
